### 2018-03-20 mftpc/pants-intro.tex
mftpc/pants-intro: Import corresponding to 2018-3

\begin{switch}
\item{BY\_A\_SINGLE\_THREAD}:
  Attempt to repair your pants using a single thread.
  \goto{pants-single}
\item{WITH\_HT\_TECHNOLOGY}:
  Find another thread-like object with which to repair your pants.
  \goto{pants-multi}
\end{switch}

>>>>

\begin{switch}
\item{BY\_A\_SINGLE\_THREAD}
  Attempt to repair your pants using a single thread.
  \goto{pants-single}
\item{WITH\_HT\_TECHNOLOGY}
  Find another thread-like object with which to repair your pants.
  \goto{pants-multi}
\end{switch}
